Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-30 paper/lostanlenRelevanceScattering.tex
whitespace

It is worth mentionning that this task typically falls into a unsupervised paradigm where no prior knowldge is used to model a given scene. For each scene $s$, a model is compute $M_s$ is computed. The similarity among the scene $s_1$ and $s_2$ is computed as the similarity, see Section~\ref{sec:experiments} for further details. The BOF approach is also widely used in a supervised fashion for solving a classification task~\cite{7100934}. In this case, each class of scenes of a given typology, say \{\emph{park, boulevard, square }\}, is modeled by a GMM trained on scenes taken from a training set. In order to predict the class of a given scene $s$, the likelihood each model given the scene are computed. The scene is then labeled park if the likelihood of the GMM trained on park scenes is higher than the other likelihoods.

>>>>

It is worth mentionning that this task typically falls into a unsupervised paradigm where no prior knowldge is used to model a given scene. For each scene $s$, a model is compute $M_s$ is computed. The similarity among the scene $s_1$ and $s_2$ is computed as the similarity, see Section~\ref{sec:experiments} for further details. The BOF approach is also widely used in a supervised fashion for solving a classification task~\cite{7100934}. In this case, each class of scenes of a given typology, say \{\emph{park, boulevard, square}\}, is modeled by a GMM trained on scenes taken from a training set. In order to predict the class of a given scene $s$, the likelihood each model given the scene are computed. The scene is then labeled park if the likelihood of the GMM trained on park scenes is higher than the other likelihoods.
